---
title: "Atrial Fibrillation Management in the ED"
output: 
    html_notebook:
        code_folding: hide
        toc: yes
        toc_float: yes
        
---

```{r setup, include=FALSE}
library(tidyverse)
library(tableone)

data_tidy <- read_rds("../data/final/data_tidy.Rds")
```

## Primary Endpoint

* HR < 110 bpm within 30 minutes of first dose

```{r}
df <- data_tidy %>%
    dmap_at(c("time_dose_goal"), as.numeric) %>%
    rename("Primary_Endpoint" = primary,
           "Appropriate_First_Dose" = appropriate_dose,
           "Vitals_Checked_in_30_Min" = vital_within_30min,
           "First_Vital_After_Dose_at_Goal" = next_vital_goal,
           "Minutes_From_First_Dose_to_Goal" = time_dose_goal,
           "Percent_Time_at_Goal" = percent_goal)

vars <- c("Primary_Endpoint", 
          "Appropriate_First_Dose", 
          "Vitals_Checked_in_30_Min",
          "First_Vital_After_Dose_at_Goal",
          "Minutes_From_First_Dose_to_Goal",
          "Percent_Time_at_Goal") 

tbl <- CreateTableOne(vars = vars, strata = "med", data = df)
ptbl <- print(tbl, printToggle = FALSE)
knitr::kable(ptbl[, -4], digits = 4)
```

## Subgroup

* Among patients with an appropriate first dose

```{r}
df <- data_tidy %>%
    filter(appropriate_dose) %>%
    dmap_at(c("time_dose_goal"), as.numeric) %>%
    rename("Primary_Endpoint" = primary,
           "Vitals_Checked_in_30_Min" = vital_within_30min,
           "First_Vital_After_Dose_at_Goal" = next_vital_goal,
           "Minutes_From_First_Dose_to_Goal" = time_dose_goal,
           "Percent_Time_at_Goal" = percent_goal)

vars <- c("Primary_Endpoint", 
          "Vitals_Checked_in_30_Min",
          "First_Vital_After_Dose_at_Goal",
          "Minutes_From_First_Dose_to_Goal",
          "Percent_Time_at_Goal") 

tbl <- CreateTableOne(vars = vars, strata = "med", data = df)
ptbl <- print(tbl, printToggle = FALSE)
knitr::kable(ptbl[, -4], digits = 4)
```

* Those that had vitals checked within 30 minutes of first dose

```{r}
df <- data_tidy %>%
    filter(vital_within_30min) %>%
    dmap_at(c("time_dose_goal"), as.numeric) %>%
    rename("Primary_Endpoint" = primary,
           "Appropriate_First_Dose" = appropriate_dose,
           "First_Vital_After_Dose_at_Goal" = next_vital_goal,
           "Minutes_From_First_Dose_to_Goal" = time_dose_goal,
           "Percent_Time_at_Goal" = percent_goal)

vars <- c("Primary_Endpoint", 
          "Appropriate_First_Dose", 
          "First_Vital_After_Dose_at_Goal",
          "Minutes_From_First_Dose_to_Goal",
          "Percent_Time_at_Goal") 

tbl <- CreateTableOne(vars = vars, strata = "med", data = df)
ptbl <- print(tbl, printToggle = FALSE)
knitr::kable(ptbl[, -4], digits = 4)
```
